State of the Practice for Medical Imaging Software

### 2022-10-27 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP.tex
Updates to the threats to validity section

Below we categorize and list the threats to validity that we have identified.
The categories come from \citet{AmpatzoglouEtAl2019} and \citet{ZhouEtAl2016}.

@@

\begin{description}
    \item[Construct Validity:] ``Defines how effectively a test or experiment measures
    up to its claims. This aspect deals with whether or not the researcher measures
    what is intended to be measured'' \citep{AmpatzoglouEtAl2019}.
\end{description}

\begin{description}
    \item[Internal Validity:] ``This aspect relates to the examination of causal
    relations. Internal validity examines whether an experimental
    treatment/condition makes a difference or not, and whether there is evidence
    to support the claim'' \citep{AmpatzoglouEtAl2019}.
\end{description}

\begin{description}
    \item[External Validity:] ``Define the domain to which a study's findings
    can be generalized'' \citep{ZhouEtAl2016}.
\end{description}

\begin{description}
    \item[Conclusion Validity:] ``Demonstrate that the operations of a study
    such as the data collection procedure can be repeated, with the same
    results'' \citep{ZhouEtAl2016}.
\end{description}

>>>>

Below we categorize and list the threats to validity that we have identified.
Our categories come from an analysis of software engineering secondary studies
by \citet{AmpatzoglouEtAl2019}, where a secondary study analyzes the data from a
set of primary studies.  \citet{AmpatzoglouEtAl2019} is appropriate because a
common example of a secondary study is a systematic literature review. Our
methodology is a systematic software review --- the primary studies
are the software packages, and our work collects and analyzes these primary
studies.

\subsection{Reliability}

\subsection{Reliability}

A study is reliable if its data and analysis are independent of the specific
researcher(s) doing the study.  That is, repetition of the study by a different
researcher should achieve the same results, as long as they use the same
methodology \citep{RunesonAndHost2009}.  For our study the identified
reliability related threats include the following:

\begin{itemize}
\item In our methodology, one individual does the manual measures for all
packages. The grader's abilities, experiences, and biases may influence the
results.  
\item Completing the manual measures of all packages took place over several
months. During this time the contents of the software repositories may change
and the reviewer's judgment may drift.
\end{itemize}

We investigated the risk of reviewer dependence in previous work \citep{SmithEtAl2016}, % DOUBLE BLIND
where we demonstrated that the measurement process is
reasonably reproducible by having five products graded by a second reviewer. The
ranking via this independent review was almost identical to the original
ranking. As long as each grader uses consistent definitions, the relative
comparisons in the AHP results will be consistent between graders.

\subsection{Construct Validity}

Construct validity means that adopted metrics represent what they are intended
to measure \citep{RunesonAndHost2009}. The construct validity related threats
for the LBM study include the following:

\begin{itemize}
\item We measure our software qualities indirectly, rather than directly.
Unfortunately meaningful direct measures for qualities like maintainability,
reusability and verifiability, are not available.  Therefore, we follow the
usual approach of assuming that following procedures and adhering to standards
yields a higher-quality product \citep[p.\ 112]{VanVliet2000}.
\item The measure of surface robustness (Section~\ref{Sec_Robustness}) is only
based on two pieces of data per project. The measurement of robustness could be
expanded, as it currently only measures the impact of unexpected input. Other
intentional faults could be introduced, but this would require a larger
investment of measurement time. 
\item We may have inaccurately estimated maintainability by assuming a higher
ratio of comments to source code improves maintainability
(Section~\ref{Sec_Maintainability}). 
\item Reusability (Section~\ref{reusabilityresults}) is assessed via the number
of code files and LOC per file. While this measure is indicative of modularity,
it is possible that some packages have many files, with few LOC, but the files
do not contain source code that is easily reusable. The formatting may be poor,
or the source code may be vague and have ambiguous identifiers. 
\item The measurement of understandability
(Section~\ref{Sec_SurfUnderstandability}) relies on 10 random source code files.
By random chance, the 10 files that were chosen may not be representative. 
\item Our overall AHP ranking makes the unrealistic assumption of equal
weighting between qualities (Section~\ref{Sec_OverallQuality}).
\item Our approximation of popularity by stars and watches
(Section~\ref{repmetrics}) may not be valid. 
\end{itemize}

\subsection{Internal Validity} \label{Sec_InternalValidity}

A study is internally valid if the discovered causal relations are trustworthy
and cannot be explained by other factors \citep{RunesonAndHost2009}. The
internal validity threats include the following:

\begin{itemize}
\item We may have missed a relevant software package in our search for LBM
software packages (Section~\ref{identifysoftware}).
\item A temporal gap exists between the manual measurement of Musubi and the
measurement of all other packages (Section~\ref{filtersoftware}). This gap
caused a mismatch between the time of manual and automated data collection,
since we updated the automated measures (like the number of files, LOC, etc.)
when Musubi was added.
\item Our methodology assumes that artifacts in the repositories will show us
the approach used for software development.  However, not all activities will
necessarily leave a trace in the repositories. For instance, only three packages
(ESPResSo, Ludwig, Musubi) show evidence in their artifacts of unit testing and
CI (Section~\ref{SecSurfCorrectAndVerifiab}), even though interviews suggest a
more frequent use of both unit testing and CI. For example, OpenLB, pyLBM, and
TCLB use such methods during development despite this not being obvious from an
analysis of the online material.
\item In our manual measures of the software repositories, we may have missed
some data due to technology issues like broken links. This issue arose with the
measurement of Palabos, which had a broken link to its user manual, as noted in
Section~\ref{Sec_CompareArtifacts}. 
\item Our interviews were with a relatively small sample of four LBM developers.
The pain points (Section~\ref{painpoints}) they expressed may not be
representative of the rest of their community.
\end{itemize}

Although we found that unit testing and CI usage is likely higher than the
repository artifacts suggest, we did not change the manual measurement results.
Given that we could not interview a representative for every project, we left
the data as collected to keep our measures consistent.  Moreover, CI and unit
testing done in private should not be counted as equivalent to the public
versions we detected.  When CI and unit testing are private, they are not as
effective since they are not available for others to inspect and reproduce.

\subsection{External Validity}

External validity concerns whether the results of the study can be generalized
(applied) to other situations/cases \citep{RunesonAndHost2009}.  The scope of
our work is LBM solvers.  We are confident that our search was exhaustive and
that we did not miss any highly popular examples.  Therefore, the bulk of our
validity concerns about LBM software observations are internal
(Section~\ref{Sec_InternalValidity}), not external.  However, our hope is that
the trends observed, and the lessons learned for LBM software can be applied to
other research software.  With that in mind we identified the following threat
to external validity:

\begin{itemize}
\item Generalization of our results will not be possible if the development of
LBM software is fundamentally different from other research software.
\end{itemize}

@@
